### 2015-03-13 doc/thesis/system.tex
Adding new styles to formalize the AST

\begin{figure}[!ht]
\textbf{Abstract Syntax}\\
\dstart
$$
\begin{array}{rl}
s ::= & \;\; \mathbf{skip} \; | \;
s_{1} \; ; \; s_{2} \; | \;
\overline{l} = el \; | \;
m \; | \;
\mathbf{while} \; e \; \mathbf{do} \; s \; | \;
\mathbf{if} \; e \; \mathbf{then} \; s_{1} \; \mathbf{else} \; s_{2}\\
& | \; \mathbf{local} \; \overline{id{:}T} = el \; \mathbf{in} \; s \; | \;
\mathbf{local} \; \overline{id} = el \; \mathbf{in} \; s \; | \;
\mathbf{rec} \; id{:}T = f \; \mathbf{in} \; s\\
& | \; \mathbf{return} \; el \; | \;
\lfloor a \rfloor_{0}\\
e ::= & \;\; \mathbf{nil} \; | \;
k \; | \;
id \; | \;
e_{1}[e_{2}] \; | \;
{<}T{>} \; id \; | \;
f \; | \;
\{ \; \overline{p} \; \} \; | \;
\{ \; \overline{p},me \; \} \; | \;
e_{1} + e_{2} \; | \;
e_{1} \; {..} \; e_{2} \\
& | \; e_{1} == e_{2} \; | \;
e_{1} < e_{2} \; | \;
e_{1} \;\&\; e_{2} \; | \;
e_{1} \; \mathbf{and} \; e_{2} \; | \;
e_{1} \; \mathbf{or} \; e_{2} \; | \;
\mathbf{not} \; e \; | \;
\# \; e \; | \;
\lfloor me \rfloor_{1}\\
l ::= & \;\; id_{l} \; | \;
e_{1}[e_{2}] \; | \;
id[k] \; {<}T{>}\\
k ::= & \;\; \mathbf{false} \; | \;
\mathbf{true} \; | \;
{\it int} \; | \;
{\it float} \; | \;
{\it string}\\
p ::= & \;\; [e_{1}] = e_{2}\\
el ::= & \;\; \overline{e} \; | \;
\overline{e}, me\\
me ::= & \;\; a \; | \;
{...}\\
a ::= & \;\; e(el) \; | \;
e{:}n(el)\\
m ::= & \;\; \mathbf{fun} \; id_{1}{:}id_{2} \; (\overline{id{:}T}){:}S \; fb \; | \;
\mathbf{fun} \; id_{1}{:}id_{2} \; (\overline{id{:}T},{...}{:}T){:}S \; fb\\
f ::= & \;\; \mathbf{fun} \; (\overline{id{:}T}){:}S \; fb \; | \;
\mathbf{fun} \; (\overline{id{:}T},{...}{:}T){:}S \; fb\\
fb ::= & \;\; s \;;\; \mathbf{return} \; el\\
id ::= & \;\; {\it name}\\
\end{array}
$$
\dend
\caption{Typed Lua abstract syntax}
\label{fig:syntax}
\end{figure}

>>>>

\begin{figure}[!ht]
\textbf{Abstract Syntax}\\
\dstart
$$
\begin{array}{rl}
s ::= & \;\; \mathbf{skip} \; | \;
s_{1} \; ; \; s_{2} \; | \;
\overline{l} = el \; | \;
m \; | \;
\mathbf{while} \; e \; \mathbf{do} \; s \; | \;
\mathbf{if} \; e \; \mathbf{then} \; s_{1} \; \mathbf{else} \; s_{2}\\
& | \; \mathbf{local} \; \overline{id{:}T} = el \; \mathbf{in} \; s \; | \;
\mathbf{local} \; \overline{id} = el \; \mathbf{in} \; s \; | \;
\mathbf{rec} \; id{:}T = f \; \mathbf{in} \; s\\
& | \; \mathbf{return} \; el \; | \;
\lfloor a \rfloor_{0}\\
e ::= & \;\; \mathbf{nil} \; | \;
k \; | \;
id \; | \;
e_{1}[e_{2}] \; | \;
{<}T{>} \; id \; | \;
f \; | \;
\{ \; \overline{[e_{1}] = e_{2}} \; \} \; | \;
\{ \; \overline{[e_{1}] = e_{2}},me \; \} \\
& | \; e_{1} + e_{2} \; | \;
e_{1} \; {..} \; e_{2} \; | \;
e_{1} == e_{2} \; | \;
e_{1} < e_{2} \; | \;
e_{1} \;\&\; e_{2} \; | \;
e_{1} \; \mathbf{and} \; e_{2} \; | \;
e_{1} \; \mathbf{or} \; e_{2} \\
& | \; \mathbf{not} \; e \; | \;
\# \; e \; | \;
\lfloor me \rfloor_{1}\\
l ::= & \;\; id_{l} \; | \;
e_{1}[e_{2}] \; | \;
id[k] \; {<}T{>}\\
k ::= & \;\; \mathbf{false} \; | \;
\mathbf{true} \; | \;
{\it int} \; | \;
{\it float} \; | \;
{\it string}\\
el ::= & \;\; \overline{e} \; | \;
\overline{e}, me\\
me ::= & \;\; a \; | \;
{...}\\
a ::= & \;\; e(el) \; | \;
e{:}n(el)\\
m ::= & \;\; \mathbf{fun} \; id_{1}{:}id_{2} \; (pl){:}S \; s \;;\; \mathbf{return} \; el\\
f ::= & \;\; \mathbf{fun} \; (pl){:}S \; s \;;\; \mathbf{return} \; el\\
pl ::= & \;\; \overline{id{:}T} \; | \;
\overline{id{:}T},{...}{:}T\\
\end{array}
$$
\dend
\caption{Typed Lua abstract syntax}
\label{fig:syntax1}
\end{figure}

\begin{figure}[!ht]
\textbf{Abstract Syntax}\\
\dstart
$$
\begin{array}{rlr}
s ::= & & \textsc{statements:}\\
& \;\; \mathbf{skip} \;
| \; s_{1} \; ; \; s_{2} \;
| \; \overline{l} = el & \\
& | \; \mathbf{while} \; e \; \mathbf{do} \; s \;
| \; \mathbf{if} \; e \; \mathbf{then} \; s_{1} \; \mathbf{else} \; s_{2} & \\
& | \; \mathbf{local} \; \overline{id{:}T} = el \; \mathbf{in} \; s \;
| \; \mathbf{local} \; \overline{id} = el \; \mathbf{in} \; s & \\
& | \; \mathbf{rec} \; id{:}T = f \; \mathbf{in} \; s \;
| \; \mathbf{return} \; el \;
| \; \lfloor a \rfloor_{0} & \\
& | \; \mathbf{fun} \; id_{1}{:}id_{2} \; (pl){:}S \; s \;;\; \mathbf{return} \; el & \\
e ::= & & \textsc{expressions:}\\
& \;\; \mathbf{nil} \;
| \; k \;
| \; id \;
| \; e_{1}[e_{2}] \;
| \; {<}T{>} \; id \;
| \; f & \\
& | \; \{ \; \overline{[e_{1}] = e_{2}} \; \} \;
| \; \{ \; \overline{[e_{1}] = e_{2}},me \; \} & \\
& | \; e_{1} + e_{2} \;
| \; e_{1} \; {..} \; e_{2} \;
| \; e_{1} == e_{2} \;
| \; e_{1} < e_{2} & \\
& | \; e_{1} \;\&\; e_{2} \;
| \; e_{1} \; \mathbf{and} \; e_{2} \;
| \; e_{1} \; \mathbf{or} \; e_{2} \;
| \; \mathbf{not} \; e \;
| \; \# \; e & \\
& | \; \lfloor me \rfloor_{1} & \\
l ::= & & \textsc{left-hand values:}\\
& \;\; id_{l} \; | \;
e_{1}[e_{2}] \; | \;
id[k] \; {<}T{>} & \\
k ::= & & \textsc{literal constants:}\\
& \;\; \mathbf{false} \; | \;
\mathbf{true} \; | \;
{\it int} \; | \;
{\it float} \; | \;
{\it string} & \\
el ::= & & \textsc{expression lists:}\\
& \;\; \overline{e} \; | \;
\overline{e}, me & \\
me ::= & & \textsc{multiple results:}\\
& \;\; a \; | \;
{...} & \\
a ::= & & \textsc{applications:}\\
& \;\; e(el) \; | \;
e{:}n(el) & \\
f ::= & & \textsc{function declarations:}\\
& \;\; \mathbf{fun} \; (pl){:}S \; s \;;\; \mathbf{return} \; el & \\
pl ::= & & \textsc{parameter lists:}\\
& \;\; \overline{id{:}T} \; | \;
\overline{id{:}T},{...}{:}T & \\
\end{array}
$$
\dend
\caption{Typed Lua abstract syntax}
\label{fig:syntax2}
\end{figure}

\begin{figure}[!ht]
\textbf{Abstract Syntax}\\
\dstart
$$
\begin{array}{rlr}
s ::= & & \textsc{statements:}\\
& \;\; \mathbf{skip} \;
| \; s_{1} \; ; \; s_{2} & \textit{skip and sequence}\\
& | \; \overline{l} = el & \textit{multiple assignment}\\
& | \; \mathbf{while} \; e \; \mathbf{do} \; s \;
| \; \mathbf{if} \; e \; \mathbf{then} \; s_{1} \; \mathbf{else} \; s_{2} & \textit{control flow}\\
& | \; \mathbf{local} \; \overline{id{:}T} = el \; \mathbf{in} \; s \;
| \; \mathbf{local} \; \overline{id} = el \; \mathbf{in} \; s & \textit{variable declaration}\\
& | \; \mathbf{rec} \; id{:}T = f \; \mathbf{in} \; s & \textit{recursive function} \\
& | \; \mathbf{return} \; el & \textit{return} \\
& | \; \lfloor a \rfloor_{0} & \textit{application with no results}\\
& | \; \mathbf{fun} \; id_{1}{:}id_{2} \; (pl){:}S \; s \;;\; \mathbf{return} \; el & \textit{method declaration}\\
e ::= & & \textsc{expressions:}\\
& \;\; \mathbf{nil} \;
| \; k & \textit{nil and other literals}\\
& | \; id & \textit{variable reading}\\
& | \; e_{1}[e_{2}] & \textit{table reading}\\
& | \; {<}T{>} \; id & \textit{type coercion}\\
& | \; f & \textit{function declaration}\\
& | \; \{ \; \overline{[e_{1}] = e_{2}} \; \} \;
| \; \{ \; \overline{[e_{1}] = e_{2}},me \; \} & \textit{table constructor}\\
& | \; e_{1} + e_{2} \;
| \; e_{1} \; {..} \; e_{2} \;
| \; e_{1} == e_{2} \;
| \; e_{1} < e_{2} & \textit{binary operations}\\
& | \; e_{1} \;\&\; e_{2} \;
| \; e_{1} \; \mathbf{and} \; e_{2} \;
| \; e_{1} \; \mathbf{or} \; e_{2} & \textit{binary operations}\\
& | \; \mathbf{not} \; e \;
| \; \# \; e & \textit{unary operations} \\
& | \; \lfloor me \rfloor_{1} & \textit{expressions with one result}\\
l ::= & & \textsc{left-hand values:}\\
& \;\; id_{l} & \textit{variable writing}\\
& | \; e_{1}[e_{2}] & \textit{table writing}\\
& | \; id[k] \; {<}T{>} & \textit{type coercion}\\
k ::= & & \textsc{literal constants:}\\
& \;\; \mathbf{false} \; | \;
\mathbf{true} \; | \;
{\it int} \; | \;
{\it float} \; | \;
{\it string} & \\
el ::= & & \textsc{expression lists:}\\
& \;\; \overline{e} \; | \;
\overline{e}, me & \\
me ::= & & \textsc{multiple results:}\\
& \;\; a & \textit{application}\\
& | \; {...} & \textit{vararg expression}\\
a ::= & & \textsc{applications:}\\
& \;\; e(el) & \textit{function application}\\
& | \; e{:}n(el) & \textit{method application}\\
f ::= & & \textsc{function declarations:}\\
& \;\; \mathbf{fun} \; (pl){:}S \; s \;;\; \mathbf{return} \; el & \\
pl ::= & & \textsc{parameter lists:}\\
& \;\; \overline{id{:}T} \; | \;
\overline{id{:}T},{...}{:}T & \\
\end{array}
$$
\dend
\caption{Typed Lua abstract syntax}
\label{fig:syntax}
\end{figure}
